Flatiron cleaning

### 2021-11-18 Rmd/rdi analysis.Rmd
Add question, ready for live modif and add HR adjusted by drug

### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" #& 
           # ismaintenancetherapy == "FALSE"
         ) %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()
```
We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis. Patients left :

@@

### step 2: 90 days rule between diagnosis and treatment

@@

### step 3: 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis

@@

### step 4: Exclude exclude == "1" coded by Lauren

@@

### step 5: Remove chemotherapy only patients
```{r}
drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))
drugs1 %>% distinct(patientid) %>% nrow()
```

### step 5: Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate, ismaintenancetherapy) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

### step 6: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = 
           factor(chemotherapy_type, levels = 
                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = first(episodedate)) %>% 
  mutate(lineenddate_new = last(episodedate)) %>% 
  ungroup() %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

@@

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(had_neo, had_adj, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(had_neo ~ "dichotomous", 
                          had_adj ~ "dichotomous"),
              missing = "no")
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

@@

<!-- ### step : remove patients with adj too far from surgery -->
```{r}
# remove_delayed_drug <- therapy_line %>% 
#   mutate(interval = case_when(
#     chemotherapy_type == "Adjuvant" & 
#       linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
#   ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
#   filter(interval > 3) %>% 
#   distinct(patientid, .keep_all = TRUE)
# remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")
# 
# therapy_line <- therapy_line %>% 
#   # Remove patients with more than 1 line as Neo
#   filter(!str_detect(patientid, remove_delayed_drug))
# therapy_line %>% distinct(patientid) %>% nrow()

### step 8: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("check")`

remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, remove_morethan1_neo))
```

### step 7: Remove linename that doesn't include platinum or taxanes in first line

@@

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

# therapy_line %>% distinct(patientid) %>% nrow()
```

@@

@@

For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
  theme_minimal(base_size = 14)+
  labs(x="Line duration", 
       y="Number of Patient",
       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)

```
Several patients have a short line.  
`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, surgerydate, episodedate, line_duration, drugname,
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, linenumber_adj) %>% 
  filter(line_duration < 30) %>% 
  arrange(line_duration, patientid, episodedate)
```

@@

### step 9: Remove patients who switch drug within a line

@@

`r emo::ji("question_mark")`
<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
```{r}
therapy_line %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, linename) %>% 
  tbl_summary(by = linename)
```

@@

### step 10: Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394

@@

  # Look at dose dense
  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
  mutate(dose_dense = n()) %>% 
  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
  ungroup() # %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense,
  #        is_dose_dense,cycle_major_drugname, cycle_drugname,
  #        cycle_count_perline, cycle_major_drugname, drugname_count_perline, cycle_start_date) #%>%  # F002DD2953889, F003F2BEEDB37 only 1+2

@@

# Remove too much cycle
```{r remove more than 9 cycle patients}
therapy_cycle %>% 
  filter(linenumber_new == 1) %>% 
  arrange(patientid, linenumber_new, desc(dose_dense)) %>% 
  mutate(dose_dense = as.factor(dose_dense)) %>%  # too much cycle
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(dose_dense, linename) %>% 
  tbl_summary(by = linename)

too_much_cycle <- therapy_cycle %>%
  filter(
    (therapy == "Upfront Surgery" & total_cycle_increment > 9) |
      (therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant" & total_cycle_increment > 9)
  ) %>%
  distinct(patientid)
too_much_cycle <- paste(too_much_cycle$patientid, collapse = "|")

therapy_cycle <- therapy_cycle %>%
  # remove these patients who switched C > C
  filter(!str_detect(patientid, too_much_cycle))
therapy_cycle %>% distinct(patientid) %>% nrow()
```

### step 11: Bind everything together and calculating target_auc and expected dose

@@

tbl_stack(list(tbl1, tbl2),
          group_header = c(
                           "paclitaxel/Upfront Surgery", 
                           "paclitaxel/Upfront Chemo"),
          quiet = TRUE)
```
<br>

@@

>>>>

### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" #& 
           # ismaintenancetherapy == "FALSE"
         ) %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()
```
We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis. Patients left :

@@

### step 2: Flatiron recommendation cleanup
#### 90 days rule between diagnosis and treatment

@@

#### 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis

@@

#### Exclude exclude == "1" coded by Lauren

@@

### step 3: Remove chemotherapy only patients
```{r}
drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))
drugs1 %>% distinct(patientid) %>% nrow()
```

#### Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory)) %>%

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, 
           drugname, units, surgerydate, days_at_first_drug, days_at_surg, 
           diagnosisdate, ismaintenancetherapy) %>%
  summarise_at(vars(route, amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  mutate(route = case_when(
    str_detect(route, ";")            ~ "Intravenous",
    TRUE                              ~ route
  )) %>% 
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

#### Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = 
           factor(chemotherapy_type, levels = 
                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
  group_by(patientid, linenumber_new) %>% 
  mutate(linestartdate_new = min(episodedate)) %>% 
  mutate(lineenddate_new = max(episodedate)) %>% 
  ungroup() %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

@@

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(had_neo, had_adj, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(had_neo ~ "dichotomous", 
                          had_adj ~ "dichotomous"),
              missing = "no")
# therapy_line %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(therapy, treatment_sequence) %>% 
#   tbl_summary(by = therapy)
```

@@

### step 4: Remove linename that doesn't include platinum or taxanes in first line

@@

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```

@@

### step 5: remove patients with maintenance as first line adjuvant?????
`r emo::ji("question_mark")`
<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
```{r}
therapy_line %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, linename) %>% 
  tbl_summary(by = linename)
therapy_line %>% 
  filter(linenumber_adj == 1) %>%
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
therapy_line %>% 
  filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant") %>%
  arrange(desc(ismaintenancetherapy)) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(ismaintenancetherapy, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
```

#### remove only the maintenance line in neo or adj
```{r remove only the maintenance line in neo or adj}
# therapy_line <- therapy_line %>% 
#   filter(!(ismaintenancetherapy == TRUE & linenumber_adj == 1))
# therapy_line %>% distinct(patientid) %>% nrow()
```

#### OR remove patients with maintenance in neo
```{r remove patients with maintenance in neo}
# remove_neo_patients_maintenance <- therapy_line %>% 
#   filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant", ismaintenancetherapy == TRUE) %>%
#   arrange(desc(ismaintenancetherapy)) %>% 
#   distinct(patientid)
# 
# therapy_line <- therapy_line %>%
#   filter(!str_detect(patientid, paste(remove_neo_patients_maintenance$patientid, collapse = "|")))
# therapy_line %>% distinct(patientid) %>% nrow()
```

#### OR remove totally patients with maintenance in frontline neo or adj
```{r remove totally patients with maintenance in neo or adj}
remove_patients_maintenance <- therapy_line %>% 
  filter(linenumber_adj == 1 & ismaintenancetherapy == TRUE) %>%
  arrange(desc(ismaintenancetherapy)) %>% 
  distinct(patientid)

therapy_line <- therapy_line %>%
  filter(!str_detect(patientid, paste(remove_patients_maintenance$patientid, collapse = "|")))
therapy_line %>% distinct(patientid) %>% nrow()
```

### step 6: remove patients with long gap between surgery and adjuvant start ????
Depending on the answers:

#### remove patients with more than 9 cycles total in upfront chemo or upfront surgery
Did a gap of 3 months
```{r}
remove_delayed_drug <- therapy_line %>%
  mutate(interval = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
    ),
  ) %>% 
  arrange(patientid, episodedate) %>%
  filter(interval > 3) %>%
  distinct(patientid, .keep_all = TRUE)

therapy_line <- therapy_line %>%
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, paste(remove_delayed_drug$patientid, collapse = "|")))
therapy_line %>% distinct(patientid) %>% nrow()
```

### step 7: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("check")`

remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1) %>% 
  distinct(patientid)

therapy_line <- therapy_line %>% 
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, paste(remove_morethan1_neo$patientid, collapse = "|")))
```

@@

For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  # select(patientid, linenumber, linenumber_new, linenumber_adj, 
  #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_histogram(color = "slateblue", aes(fill = route), binwidth = 7) +
  theme_minimal(base_size = 14)+
  labs(x="Line duration", 
       y="Number of Patient",
       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
```
Several patients have a short line.  
`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle** We said during October meeting to check at IP

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, surgerydate, episodedate, line_duration, drugname,
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, route, amount) %>% 
  filter(line_duration < 30) %>% 
  arrange(line_duration, patientid, episodedate)
```

#### Remove peritoneal administration
```{r}
therapy_line <- therapy_line %>% 
  filter(route == "Intravenous")
```

@@

### step 8: Remove patients who switch drug within a line

@@

@@

#### Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394

@@

  # Look at dose dense
  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
  mutate(dose_dense = n()) %>% 
  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
  ungroup() # %>% 
  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense, amount, ismaintenancetherapy,
  #        is_dose_dense,cycle_major_drugname, cycle_drugname,
  #        cycle_count_perline, cycle_major_drugname, drugname_count_perline, cycle_start_date) #%>%  # F002DD2953889, F003F2BEEDB37 only 1+2

@@

### step 9: Remove too much cycle
```{r more than 9 cycle patients}
therapy_cycle %>% 
  filter(therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
therapy_cycle %>% 
  filter(therapy == "Upfront Surgery") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
```
We said to remove patients with more than 9 total cycle but maybe we can save some....

#### What is dose dense / or unnoted maintenance (example in ppt) 
2 in the dose dense would mean 1 carbo + 2 pacli  
3 in the dose dense would mean 1 carbo + 3 pacli  
etc
```{r what is dose dense}
therapy_cycle %>% 
  filter(linenumber_adj == 1) %>% 
  arrange(patientid, linenumber_new, desc(dose_dense)) %>% 
  mutate(dose_dense = as.factor(dose_dense)) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(dose_dense, linename) %>% 
  tbl_summary(by = linename)
```

#### Remove wrong dose dense patients (>3) ???
```{r remove wrong dose dense patients}
wrong_dose_dense <- therapy_cycle %>% 
  filter(linenumber_adj == 1 & dose_dense > 3) %>% 
  distinct(patientid)

therapy_cycle <- therapy_cycle %>%
  filter(!str_detect(patientid, paste(wrong_dose_dense$patientid, collapse = "|")))
therapy_cycle %>% distinct(patientid) %>% nrow()
```

#### OR Remove only the extra administration from 1+3 dose dense???
```{r remove only the extra administration from 1+3 dose dense}
therapy_cycle <- therapy_cycle %>%
  filter(dose_dense <= 3)
therapy_cycle %>% distinct(patientid) %>% nrow()
```

#### Then
#### Remove totally the patients with more than 9 cycle total
```{r more than 9 cycle patients same code}
therapy_cycle %>% 
  filter(therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
therapy_cycle %>% 
  filter(therapy == "Upfront Surgery") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type)
```

```{r remove more than 9 cycle patients}
too_much_cycle <- therapy_cycle %>%
  filter(
    (therapy == "Upfront Surgery" & total_cycle_increment > 9) |
      (therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant" & total_cycle_increment > 9)
  ) %>%
  distinct(patientid)

therapy_cycle <- therapy_cycle %>%
  # remove these patients who switched C > C
  filter(!str_detect(patientid, paste(too_much_cycle$patientid, collapse = "|")))
therapy_cycle %>% distinct(patientid) %>% nrow()
```

#### OR remove only the extra cycle????
```{r remove only the extra cycle}
therapy_cycle <- therapy_cycle %>%
  filter(total_cycle_increment <= 9)
therapy_cycle %>% distinct(patientid) %>% nrow()
```

### step 10: Bind everything together and calculating target_auc and expected dose

@@

####
tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & 
                               therapy == "Upfront Surgery" &
                               dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(drugname == "paclitaxel" & 
                               therapy == "Upfront Chemo" &
                               dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl5 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
tbl6 <- tbl_merge(list(tbl2, tbl4))

tbl_stack(list(tbl5, tbl6),
          group_header = c(
                           "paclitaxel/Upfront Surgery", 
                           "paclitaxel/Upfront Chemo"),
          quiet = TRUE)
```
<br>

<span style="color:green">**Taxanes dose dense**</span>

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
Frontline_adjusted <- Frontline %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo, RDI_carbo_grp, RDI_carbo_grp1, RDI_pacli, RDI_pacli_grp, RDI_pacli_grp1, .direction = "downup") %>% 
  distinct(patientid, .keep_all = TRUE)
